Long-range Interatomic Coulombic Decay in ArXe clusters: Experiment and Theory

### 2016-08-05 letters/reply_referee.tex

  \item \emph{Page 29:
        the efficiency of ICD is found below unity for clusters having few Xe atoms. I guess this is because in these clusters ICD and ETMD are closed for some Argon atoms which are anyway ionized. Maybe a statistical model may explain it. The theory could also help since it should be easy to determine the efficiency for all clusters considered in this study.}\vspace{0.3cm}\\
        This is a good point from the referee. We have included a short discussion of the possible explanations of this effect at the respective place: {\color{blue}{In clusters with a low Xe content we can assume that there are Ar atoms that have distances to the next Xe atom that are too large for autoionization to occur. This is especially the case if we have very large clusters that show segregation of Ar and Xe atoms. If we decrease the cluster size, this effect should play a minor role because large distances are not available here. However, with decreasing cluster size, the number of homogeneous clusters in the cluster beam increases. In fact, at small cluster sizes, the size distribution has its maximum at the monomer. This increasing number of homogeneous Ar clusters still show Ar 3s intensity but do not contribute to recorded coincidences because they cannot autoionize. }}

\end{enumerate}

\textbf{Referee \#2} raised the following points:

\begin{enumerate}
 \item \emph{ETMD(3) should be explained in the introduction by a sentence or two to aid the reader (at the moment, it is first explained in the theory section).
}\vspace{0.3cm}\\
       It was indeed explained already but in wording specific to
       experimentalists. We therefore changed the last paragraph on page 3 to:\\
       Soon after, related autoionization processes were discovered
       {\color{blue}{in which the initial vacancy is filled by an electron from a neighbouring unit. These were termed `Electron Transfer Mediated Decay'
(ETMD)$^{9–12}$. If the excess energy is transferred to a third unit which is subsequently ionized, the process is called ETMD(3), if the electron donor is ionized once more the process is called ETMD(2) and if the excess energy is used to ionize the initially ionized unit the process is called `exchange ICD'$^{13,14}.$}}

 \item \emph{The authors mention that the ‘nuclear dynamics may play an important role’ but that they have been neglected in the calculations. While I understand that it is not feasible in such large systems the authors should at least briefly discuss the possible effect of nuclear dynamics e.g. peak shifts, broadening, ICD vs. ETMD, etc. }\vspace{0.3cm}\\
       We added two paragraphs at the end of the theoretical results section
       discussing the possible effects of nuclear dynamics:\\
       {\color{blue}{All these results neglect the effect of nuclear dynamics, which might affect the spectra. Possible reasons are distance dependend channel closings and openings, a different distribu- tion of interatomic distances due to vibrations and their different impact on the ICD and the ETMD(3). E.g., for the ICD in the neon dimer, the treatment of nuclear dynamics increases the decay width by approximately a factor 2.$^{57}$ However, the atomic displacement can be expected to be by far less severe in clusters than in dimers or trimers. Additionally, the
elongation of one interatomic distance in a cluster automatically results in the shortening of a different interatomic distance, which will reduce the overall effect. Therefore, there will be a broader spectrum charges in the final state d resulting in a broadening of the peak. This was taken into account by folding the stick spectrum with Gaussians with a width of 300 meV and 600meV for the ICD and ETMD(3), respectively. While the width of the ICD peaks was estimated from the potential energy surface of the ArXe dimer, the situation is more complex in case of the ETMD(3) with three degrees of freedom involved. It was therefore guessed to be twice the width of the ICD peak.
The channel closing due to shortening of the interatomic distance is not relevant for the ETMD(3) process in the ArXe clusters, treated in this work, because this would require unnaturally short interatomic distances. However, for the ICD it might result in a lower number of pairs with open decay channels and hence decrease the decay width. Since the folded peaks are constituted from several pairs of different distances, it would result in a slight peak shift to higher energies of the combined peak at lowest energy. For a more detailed discussion of nculear dynamics for the ICD in dimers vs. in clusters see Ref 58.}}

### 2016-08-05 intro.tex
last points

Soon after, related 
autoionization processes were discovered that are governed by a
charge transfer instead of an energy transfer. 
These were termed `Electron Transfer Mediated Decay' 
 (ETMD),\cite{zobeley,mueller,sakai,foerstel} for transitions in 
 which the originally excited site is neutralized by the decay 
and `exchange ICD' for charge transfer contributions to the 
normal ICD amplitude.\cite{santrarev,jahnkesat}

>>>>

Soon after, related 
autoionization processes were discovered
in which the initial vacancy is filled by an electron from a neighbouring unit.
These were termed `Electron Transfer Mediated Decay' 
 (ETMD),\cite{zobeley,mueller,sakai,foerstel}.
If the excess energy is transferred to a third unit which is subsequently
ionized, the process is called ETMD(3), if the electron donor is ionized once
more the process is called ETMD(2) and if the excess energy is used to
ionize the initially ionized unit the process is called
`exchange ICD'. \cite{santrarev,jahnkesat}
